### 2015-12-10 Projects/DelCo_2012/Report/DelCo_2012.tex
edits to DelCo 2012

>>>>

To compare the effectiveness of the suppression agents (CAFS, water), the temperatures from the thermocouple tree which was not directly impacted by the streams was analyzed. Thermocouples that were greater than 2.13~m (7~ft) below the ceiling (the bottom 3 thermocouples) were not included because of the minimal temperature readings throughout the tests. Gas cooling was determined by taking the normalized maximum change in temperature ($\hat{T}$) over the test interval ($T_{max}$ is peak temperature before suppression and $T_{min}$ is minimum temperature after suppression):
\begin{equation}
\label{eq:norm_temp}
\hat{T} = \frac{T_{max}-T_{min}}{T_{max}}
\end{equation}
The normalized temperature difference is taken because of the large variation in pre-suppression temperature within replicates of a particular suppression agent and between suppression agents.
